### 2017-06-15 src/5_3_Proposal.tex
change tittle
Intro 5-3 ready

\chapter{Real-time intraday Forex rates forecasting using a regularized Vector
Error Correction model}

Vector error correction model (VECM) parameters are commonly obtained using the
ordinary least squares method. Since this parameters could be sensitive to the
data, this proposal is to get these parameters using ridge regression which
could lead to a better generalization capability. In order to give with a
real-time response, an online version of VECM (OVECM) is proposed. OVECM solves
VECM considering only a sliding window of historical data and therefore
better response times could be achieved.

>>>>

\chapter{A Regularized Time Varying Vector Error Correction Model}

In the last chapter, the Online Vector Error Correction Model (OVECM) was proposed. OVECM parameters are obtained using the Ordinary Least Squares (OLS) method. Even though OLS is extensively used, it has over-fitting issues and is computationally expensive. Therefore, OVECM parameters could be very sensitive to the data. Ridge Regression (RR)  is commonly used
instead of OLS to tackle this problem, introducing a regularization parameter which could improve
prediction error.
In this chapter, the use of Ridge Regression (RR) and its variant called Aggregating Algorithm for Regression (AAR) is explored in order to get better generalisation capability.
